---
title: "Optimization Module"
author: "Fernando"
date: "2023-02-03"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Solving Linear Programming with R


### Library **lpSolve**

**Description:** Lp_solve is freely available (under LGPL 2) software for
solving linear, integer and mixed integer programs. This
implementation supplies a ``wrapper'' function in C and some R
functions that solve general linear/integer problems,
assignment problems, and transportation problems. 

Version: 5.6.17

[Click here to read more about the documentation](http://cran.nexr.com/web/packages/lpSolve/lpSolve.pdf)

### **5.2. Lesson-Optimisation with Excel's Solver: Part 1/Task 1** 

Let’s consider the following scenario.

A car manufacturer produces two types of cars called Edison and Yamato. Each year the company receives **8 000 blocks of steel** (one block per car). **The first car (Edison) yields a 40 000 USD per unit profit**. The second one, due to unfavorable contracts signed by the company, generates a negative **profit of -10 000 USD per unit**. The company has an order for **1 000 Yamato cars from the government that must be fulfilled**.

Since the profit of Yamato cars is negative, its production cannot be too large. Therefore, it’s assumed that the production of Yamato cars cannot be **larger than 250% of Edison’s production plus 1 000 units**. The factory is also unwilling to produce **more than one Yamato car per three Edison cars**. Given conditions provide optimal production (quantity of each vehicle produced) that maximizes the profit given the constraints.

``
``

#### **Objective function:** 

The function that it is desired to maximize or minimize

**x** $=$ Edison car

**y** $=$ Yamato car



$$Max(sales) = 40x - 10y$$

#### **Constraints**
1. We are contractually obligated to make 1000 to the goverment

$y \geq 1000$ 

2. Yamato cars cannot be larger than 250% of Edison’s production plus 1000 units.

$y \leq 2.5x + 1000$

3. Manufacturer is unwilling to produce more than one Yamato car per three Edison cars.

$y \geq 3x$ 

4. Company has 8000 block of steel.

$x + y \leq 8000$ 

``
``


#### **Convert the slope form equation to standard form (if needed):** 

##### **Requires some algebraic manipulation.** 
``
``
**Begin with slope form:**

$$y = mx + b$$

**End with standard form:**

$$Ax + By = C$$


$$
\begin{pmatrix}
0 & 1\\
-5 & 2\\
3 & -1\\
1 & 1
\end{pmatrix}
\begin{pmatrix}
x \\ 
y 
\end{pmatrix}
\begin{pmatrix}
1000 \\ 
2000\\
0\\
8000
\end{pmatrix}
$$
``
``
 
```{r}

```
### Load library.
```{r}
#If not installed, use the command install.package("lpSolve")
#install.packages("lpSolve")
library(lpSolve)
```


### **Objective function as a vector.** 

```{r}

Objective.in<-c(40,-10)

```
### **Construct the matrix,(Neo)**

$$\begin{pmatrix}
0 & 1\\
-5 & 2\\
3 & -1\\
1 & 1
\end{pmatrix}$$

```{r}
Const.mat<-matrix(c(0,1,-5,2,3,-1,1,1),nrow=4,byrow=TRUE)
Const.mat
```

### Create atomic vectors for your RHS of the equation. 

$$
\begin{pmatrix}
1000 \\ 
2000\\
0\\
8000
\end{pmatrix}$$

```{r}
gov_constraint<-1000
YamatoLimit_constraint<- 2000
factWillness_constraint<-0
material_constraint<-8000
```

### Create a RHS vector.

```{r}
# The inputs are the atomic vectors we created above. 
Const.rhs <-c(gov_constraint, YamatoLimit_constraint, factWillness_constraint, material_constraint)

```

### Create a vector for the _inequalities_ or constraints direction.
```{r}
Const.dir<-c(">=","<=",">=","<=")


```

### Insert values into the lp function

```{r}
#The inputs the vectors we created above. 
OptimumResults<-lp(direction="max",Objective.in, Const.mat,Const.dir, Const.rhs)
OptimumResults
```

#### The best solution

```{r}
OptimumResults$solution
```

#### **Parameters in the function above: **

**_OptimumResults<-lp(direction="max",Objective.in, Const.mat,Const.dir, Const.rhs)_**

**direction**	
Character string giving direction of optimization: "min" (default) or "max."

**objective.in**	
Numeric vector of coefficients of objective function

**const.mat**
Matrix of numeric constraint coefficients, one row per constraint, one column per variable (unless transpose.constraints = FALSE; see below).

**const.dir**
Vector of character strings giving the direction of the constraint: each value should be one of "<," "<=," "=," "==," ">," or ">=". (In each pair the two values are identical.)

#### For more info type **?lp**






